### 2017-09-10 paper/evaluation.tex
adding one-sentence explanation for RQ5
Added statistics of failures

To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
subjects from our benchmark that use parallelization \emph{by default}
(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
of test suites with enabled parallelization, as configured by project
developers, and without parallelization.
Table~\ref{tab:speedup} summarizes results.
Lines are sorted by project names.
Columns ``\emph{Group}'' and ``\emph{Subject}'' indicate, respectively,
the cost group and the name of the project.
Column ``$T_s$'' shows sequential execution time and column ``$T_p$''
shows parallel execution time.
Column ``$T_s/T_p$'' shows speedup or slowdown.
As usual, a ratio above 1x indicates speedup and a ratio below 1x
indicates slowdown.

@@

%% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
%% jvm - maven surefire nao tratava algumas exceptions que aconteciam na
%% execucao do teste, (3) timeout}
%% The script we implemented to measure time and flakiness takes a list
%% of tests classes to run as input and outputs the results (\ie, number
%% of test methods, failures, skips, and elapsed time) for each parallel
%% configuration.
%%\Comment{ To obtain parallel configurations, we implemented a script
%%  that takes a subject and a configuration label as inputs (\eg
%%  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
%%  the subject with the desired configuration. The workflow consists in
%%  copying the project directory to a new directory, finding all
%%  existing build files (\ie, \pomf{} files), and modifying all
%%  existing Maven Surefire configurations with new values for the
%%  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
%%  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
%%  manipulate XML documents. For configurations with forked JVMs
%%  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
%%  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
%%  core).  To adjust the pool of threads for parallelism within a JVM,
%%  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
%%    consider 2 as it is the number of native threads per core OR 6 as
%%    it represents 3 Cores * 2 native threads?}.To run the subjects and
%%  their respective variations (\ie, the modified versions according to
%%  the parallelism configuration), we used a similar approach as
%%  described in Figure~\ref{fig:mvn-execution} except that...  }
%% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /
%% T_{\text{p}}$), and for flakiness, we reported the rate of failing
%% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
\Jbc{Falta atualizar essa discussao....
Table~\ref{tab:rq6-table} summarizes results ordered by subject's
name. Recall that we only executed one module for each subject.
Values are averaged across multiple executions.  We did not report
standard deviations as they are very small in all cases.  Considering
flakiness, results show that 0\% of flakiness have been reported in 26
of the 60 combinations analyzed (43\% of the total) and that for seven
of the ten projects 0\% flakiness was reported in at least one of the
configurations.  The projects with flakiness in all configurations
were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.
It is worth highlighting the unfortunate case of \CodeIn{Moquette},
which manifested more than 20\% flaky tests in every configuration.
Considering time, it is noticeable from the averages, perhaps as
expected, an increasing speedup from configuration
\emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and from
configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.
}

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
  test suites of 70\% of the projects we analyzed could be run in
  parallel without manifesting any flaky tests.  In some of these
  cases, speedups were significant, ranging from 1x to 28.8x.}
\end{minipage}
}
\end{center}

>>>>

To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
subjects from our benchmark that use parallelization \emph{by default}
(see Table~\ref{tab:freqmodes-dynamic}).  We compared running times
of test suites with enabled parallelization, as configured by project
developers, and without parallelization. It is important to note that
there are no observed failures in either execution.
Table~\ref{tab:speedup} summarizes results.
Lines are sorted by project names.
Columns ``\emph{Group}'' and ``\emph{Subject}'' indicate, respectively,
the cost group and the name of the project.
Column ``$T_s$'' shows sequential execution time and column ``$T_p$''
shows parallel execution time.
Column ``$T_s/T_p$'' shows speedup or slowdown.
As usual, a ratio above 1x indicates speedup and a ratio below 1x
indicates slowdown.

@@

%% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
%% jvm - maven surefire nao tratava algumas exceptions que aconteciam na
%% execucao do teste, (3) timeout}
%% The script we implemented to measure time and flakiness takes a list
%% of tests classes to run as input and outputs the results (\ie, number
%% of test methods, failures, skips, and elapsed time) for each parallel
%% configuration.
%%\Comment{ To obtain parallel configurations, we implemented a script
%%  that takes a subject and a configuration label as inputs (\eg
%%  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
%%  the subject with the desired configuration. The workflow consists in
%%  copying the project directory to a new directory, finding all
%%  existing build files (\ie, \pomf{} files), and modifying all
%%  existing Maven Surefire configurations with new values for the
%%  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
%%  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
%%  manipulate XML documents. For configurations with forked JVMs
%%  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
%%  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
%%  core).  To adjust the pool of threads for parallelism within a JVM,
%%  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
%%    consider 2 as it is the number of native threads per core OR 6 as
%%    it represents 3 Cores * 2 native threads?}.To run the subjects and
%%  their respective variations (\ie, the modified versions according to
%%  the parallelism configuration), we used a similar approach as
%%  described in Figure~\ref{fig:mvn-execution} except that...  }
%% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /
%% T_{\text{p}}$), and for flakiness, we reported the rate of failing
%% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
Table~\ref{tab:rq6-table} summarizes results ordered by subject's
name.
Values are averaged across multiple executions.  We did not report
standard deviations as they are very small in all cases.  Considering
flakiness, we inspected a sample of 1000 logs to identify the causes
of flakiness manifested in 45 executions. Most of the cases occurred
by a race condition: approximately 97.5\% of the failures were caused
by a null reference and 1.6\% were caused by concurrent access of
unsyncronized data structures. More precisely, the manifested
exceptions were \CodeIn{ConcurrentModificationException} (0.8\%),
\CodeIn{NoSuchElementException} (0.7\%), and
\CodeIn{ArrayIndexOutOfBoundsException} (0.7\%).  In addition, we
identified 0.9\% cases of file dependencies manifested on
\CodeIn{EOFException} (0.2\%),
\CodeIn{FileSystemAlreadyExistsException} (0.2\%), and
\CodeIn{BufferOverflowException} (0.4\%).
The projects with flakiness in all configurations were \CodeIn{AWS
SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.  It is worth
highlighting the unfortunate case of \CodeIn{Moquette}, which
manifested more than 20\% flaky tests in every configuration.
Considering time, it is noticeable from the averages, perhaps as
expected, an increasing speedup from configuration
\emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and from
configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.
It is also worth mentioning that some combinations manifested slowdown
instead of speedup.
Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.
Overall, results show that 0\% of flakiness have been reported in 30
of the 75 (=5x15) parallelism combinations analyzed (40\% of the
total) and that for 11 of the 15 projects 0\% flakiness was
reported in at least one of the configurations.

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
  test suites of 73.33\% of the projects we analyzed could be run in
  parallel without manifesting any flaky tests.  In some of these
  cases, speedups were significant, ranging from 1x to 28.8x.}
\end{minipage}
}
\end{center}
